Supplement to *Salmonella* Environmental Persistence Informs Management Relevant to Avian and Public Health for a Data Analysis Project

### 2023-05-04 5. Manuscript/Manuscript.qmd
Updates for Final

The data selected for my MADA project is persistence and prevalence data
from two trial studies. The first trial was conducted in South Florida
where picnic tables, under the same pavilion and exposed to conditions
known to affect *Salmonella*, were selected, swabbed daily for a week
and shipped back to the University of Georgia for *Salmonella*
isolation. The second trial was conducted in Athens, Georgia, at
Whitehall Forest in a modified shade house. Bird feeders of different
materials (e.g., cedar, plastic, plastic coated, and wood coated) were
hung in triplicate and seeded with an isolate of *S.* Typhimurium
isolated from a songbird.

@@

The Picnic Table Trial data is composed of several worksheets embedded
in one excel file. After viewing the file (and running it below), there
seems to be 192 observations. I am not sure how the Picnic Table Trial
was collected but hope to visit with Dr. Hernandez regarding data
collection methods soon. Feeder Trial data was collected and noted upon
confirmation of *Salmonella* from processed samples. There are 144
observations for the Feeder Trial which spanned nearly 2 months. For
both trials, we were attempting to measure *Salmonella* persistence. The
Picnic Table Trial collected data in an attempt to measure prevalence as
well. (Please Note: Aforementioned data was imported under "Data import
and cleaning" section.)

@@

Our Feeder trial aimed to assess the persistence of *Salmonella* on four
types of feeders (cedar, plastic, cedar + antimicrobial coating, and
plastic + antimicrobial coating) in Georgia. 18 g of fresh chicken feces
was collected, homogenized, 1 g was aliquoted into individual 15 mL test
tubes, then sterilized through autoclaving. The individual alioquots
were then inoculated with 1.5x10\^7 mL of a *Salmonella* Typhimurium
isolate responsible for a previous avian salmonellosis outbreak. Samples
were then transported to a modified shade house at Whitehall Forest
where four feeder types, represented in triplicate and randomized, were
seeded with 1 g of inoculated feces and 0.5 mL of sterile physiologic
saline. Feeders were then swabbed daily for one week, every other day
for one week, and weekly for an additional week. Swabs were embedded
into 10 mL of Dulcitol Selenite broth and transported back to UGA for
processing.

>>>>

The data selected for this project is persistence and prevalence data
from two trial studies. The first trial was conducted in South Florida
where picnic tables, under the same pavilion and exposed to conditions
known to affect *Salmonella*, were selected, swabbed daily for a week
and shipped back to the University of Georgia for *Salmonella*
isolation. The second trial was conducted in Athens, Georgia, at
Whitehall Forest in a modified shade house. Bird feeders of different
materials (e.g., cedar, plastic, plastic coated, and wood coated) were
hung in triplicate and seeded with an isolate of *S.* Typhimurium
isolated from a songbird.

@@

The Picnic Table Trial data is composed of several worksheets embedded
in one excel file. After viewing the file, 192 observations were
returned. Feeder Trial data was collected and noted upon confirmation of
*Salmonella* from processed samples. The Feeder Trial data returned 144
observations for the nearly two months of sample collection. Both trials
were designed to determine the persistence of *Salmonella*. The Picnic
Table Trial also collected data in an attempt to determine prevalence.

@@

Our Feeder trial aimed to assess the persistence of *Salmonella* on four
types of feeders (cedar, plastic, cedar + antimicrobial coating, and
plastic + antimicrobial coating) in Georgia. 18 g of fresh chicken feces
was collected, homogenized, 1 g was aliquoted into individual 15 mL test
tubes, then sterilized through autoclaving. The individual alioquots
were then inoculated with 1.5x10\^7 mL of a *Salmonella* Typhimurium
isolate responsible for a previous avian salmonellosis outbreak. Samples
were then transported to a modified shade house at Whitehall Forest
where four feeder types, represented in triplicate and randomized, were
seeded with 1 g of inoculated feces and 0.5 mL of sterile physiologic
saline. Feeders were then swabbed daily for one week, every other day
for one week, and weekly for an additional week. Swabs were embedded
into 10 mL of dulcitol selenite broth and transported back to UGA for
processing.

### 2023-05-04 5. Manuscript/supplement/Supplementary_Material.qmd
Updates for Final

---
title: "Supplement to Example Manuscript Template for a Data Analysis Project"

subtitle: ""
author: Andreas Handel
date: "`r Sys.Date()`"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../dataanalysis_template_references.bib
csl: ../../vancouver.csl
---

>>>>

---
title: "Supplement to *Salmonella* Environmental Persistence Informs Management Relevant to Avian and Public Health for a Data Analysis Project"

subtitle: ""
author: Kimberly Perez
date: "`r Sys.Date()`"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../dataanalysis_template_references.bib
csl: ../../vancouver.csl
---
